\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[all]{xy}

\usepackage{amsmath,amsthm,amssymb,color,latexsym}
\usepackage{geometry}
\usepackage{physics}
\usepackage{enumerate}
\geometry{letterpaper}
\usepackage{graphicx}

\newtheorem{problem}{Problem}

\newenvironment{solution}[1][\textit{Solution}]{\textbf{#1. }}{$\blacksquare$}

\begin{document}
	\noindent EE5623701 Optimization Techniques and Applications\hfill Midterm Report\\
	Tom Van Deusen \hfill 10/14/2023

	\hrulefill

	\begin{problem}
    Prove that, given any set $\textit{C}$ and a point $\textit{x} \in \textit{C}$, the normal cone $N_C(X) = \{g: G^{T}x \geq g^{T}y, \forall y \in C\}$ is a convex set (C not necessarily convex)  
  \end{problem}
	\begin{solution}
    Let $g_{1}, g_{2} \in N_{C}(x)$, and since normal cones are convex cones,\\ 
    \begin{center}
      $(t_{1}g_{1} + t_{2}g_{2})^{T} = t_{1}g_{1}^{T}x + t_{2}g_{2}^{T}x \geq t_{1}g_{1}^{T}y + t_{2}g_{2}^{T}y = (t_{1}g_{1} + t_{2}g_{2})^{T}y, \ \forall \ t_{1}, t_{2} \geq 0$ 
    \end{center}
	\end{solution}

	\begin{problem}
    Prove that for any set \textit{C} (convex or not), its support function $I_{C}^{*}(x) = \max_{y \in C} x^{T}y$ is a convex function.
	\end{problem}
	\begin{solution}
    For every $y \in C, x^{T}y$ is a linear function of \textit{x}, so $I^{*}_{C}$ is a pointwise supremum of a family of linear functions, therefore convex.
	\end{solution}

  \begin{problem}
    Consider a closed set defined by $C = \{(x,y) | y \geq \frac{1}{1 + x^2}\}$ where $(x,y) \in \mathbb{R}^{2}$
    \begin{enumerate}
      \item Is the set \it{C} convex? (Hint: you can draw the set \it{C} on the plane to explain your answer.) 
      \item  Is the convex hull of set \it{C} also a closed set? You can also explain your answer by the plot.
    \end{enumerate}
    \begin{solution}
      \begin{enumerate}
      \item Consider the function $f(x) = \frac{1}{1 + x^{2}}$, the set $C = \textbf{epi}(f)$, i.e. $\ \forall \ y \in C, f(x) \leq y$\\ 
        Now consider $\frac{\partial}{\partial^{2}x}f(x) = \frac{6x^{2} - 2}{(1 + x^{2})^{3}}$, which is not strictly nondecreasing, which means $f(x)$ is not convex, implying $\textbf{epi}(f)$
is not convex.
      \item The closure of a the convex hull \textit{H} of a closed set \textit{C} will be \textit{H} itself, making \textit{H} closed as well.
      \end{enumerate}
    \end{solution}
  \end{problem}

  \begin{problem}
    Adapt the proof of log-deterainant function to show that $f(x) = tr(X^{-1})$ is convex on $\textbf{dom}f = S^{n}_{++}$
    \end{problem}
  \begin{solution}
    Let $\lambda_{1}, ..., \lambda_{n}$ be eigenvalues of \textit{X} and \textit{Y} be another matrix in $S^{n}_{++}$, and its eigenvalues be $\mu_{1}, ..., \mu_{n}$.
    Both $X^{-1}$ and $Y^{-1}$ so their eigenvalues are $ \frac{1}{\lambda{1}}, ..., \frac{1}{\lambda{n}}$, and $\frac{1}{\mu_{1}}, ..., \frac{1}{\mu_{n}}$, respectively.
    \\ 
    \\ 
    Consider the matrix $\theta X + (1 - \theta)Y$ for $0 \leq \theta \leq 1$, which is also positive definite because \textit(X) and \textit{Y} are positive definite, so and similar to above, the eigenvalues of $(\theta X + (1 - \theta) Y)^{-1}$ are $\frac{1}{\theta \lambda_{i} + (1 - \theta)\mu_{i}}$.
    \\ 
    \\
    So \\ 
    \\
    $\textbf{tr}(\theta X + (1 - \theta Y)) = \sum_{i=1}^{n} \frac{1}{\theta \lambda_{i} + (1 - \theta)\mu_{i}}$,
    \\
    \\ 
    and
    \\ 
    \\
    $\theta \mathbf{tr}({X^{-1}}) + (1 - \theta)\mathbf{tr}({Y^{-1}}) = \sum_{i=1}^{n} (\theta \frac{1}{\lambda_{i}} + (1 - \theta) \frac{1}{\mu_{i}})$
    \\
    \\
    And given that the function $g(x) = \frac{1}{x}$ is convex in $\mathbb{R}_{+}$, then for some $a, b \in \mathbb{R}_{+},\  0 \leq \theta \leq 1$,
    \\ 
    \\ 
    $\frac{1}{\theta a + (1 - \theta)b} \leq \theta (\frac{1}{a}) + (1 - \theta) (\frac{1}{b})$
    \\ 
    \\ 
    Applying this to the above functions, it follows that
    \\ 
    \\ 
   % $\sum_{i=1}^{n} \frac{1}{\theta \lambda_{i} + (1 - \theta)\mu_{i}} \leq \sum_{i=1}^{n} (\theta \frac{1}{\lambda_{i}} + (1 - \theta) \frac{1}{\mu_{i}}) = \sum_{i=1}^{n} \frac{1}{\theta \lambda_{i} + (1 - \theta)\mu_{i}$
    $\sum_{i=1}^{n} \frac{1}{\theta \lambda_{i} + (1 - \theta)\mu_{i}} \leq \sum_{i=1}^{n} (\theta \frac{1}{\lambda_{i}} + (1 - \theta) \frac{1}{\mu_{i}})$

  \end{solution}

  \begin{problem}
    \begin{enumerate}
      \item Prove that $f(x_1, x_2) = \frac{1}{x_{1}x_{2}}$ on $\mathbb{R}^{2}_{++}$ is convex. 
      \item Prove that $f(x_1, x_2) = \frac{x_1}{x_{2}}$  on $\mathbb{R} \times \mathbb{R}^{2}_{++}$ is convex. 
    \end{enumerate}
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Prove that $\log(\frac{e^x}{1 + e^x})$ on $\mathbb{R}$ is concave.
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Prove that, by applying Jensen’s inequality, an arithmetic mean is greater than or equal to its geometric mean, i.e., $(\prod_{i=1}^{n} x_{i})^{1/n} \leq \frac{1}{n}\sum_{i=1}^{n} x_{i}$ where $\textbf{x} \in \mathbb{R^{n}_{++}}$
  \end{problem}
  \begin{solution}
  \end{solution}
  
  \begin{problem}
    Prove that $\frac{1}{\sqrt{n}}\lVert x \rVert_{1} \leq \lVert x \rVert_{2} \leq \lVert x \rVert_{1}$
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Show that the following function $f(x)$ is convex:\\
    \begin{center}
      $f(x) = x^{T}(A(x))^{-1}x$, $\textbf{dom}{f} = \{x | A(X) \succ 0\}$
    \end{center}
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Prove that the maximum eigenvalue of a symmetric matrix is convex.
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Let $f(x) = \sum_{i=1}^{r} |x|_{[i]}$ on $\mathbb{R}^n$, where $|x|_{[i]}$ is the \it{i}-th largest component of teh absolute value of $|x|$, and $r \leq n$ is a positive number. 
    \begin{enumerate}
      \item Prove that $f(x)$ is convex.
      \item Show that $f(x) = \min_{t}(rt) + \sum_{i=1}^{n} \max(0, |x_{i} - t|)$ is convex.
    \end{enumerate}
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    Let $f(\lambda) = \textbf{x}^{T} D(\lambda)(D(\lambda) + \textbf{I})^{-1}\textbf{x} - \textbf{1}^{T}\lambda$ on $\mathbb{R}^{n}_{+}$, where $D(\lambda)$ is a diagonal matrix and $\textbf{1}^T = [1, 1, ..., 1]$.
    \begin{enumerate}
      \item Prove that $f(\lambda)$ is concave.
      \item Find the optimal value of $f(\lambda)$.
    \end{enumerate}
  \end{problem}
  \begin{solution}
  \end{solution}

 \begin{problem}
   Is the function $f(x) = ln(1 + \frac{x^2}{2 \tau^{2}_{0}})$, where $\tau_{0} > 0$, convex?
  \end{problem}
  \begin{solution}
  \end{solution}

  \begin{problem}
    \begin{enumerate}
      \item Determine whether or not $\sqrt{x_{1}x_{2}}$ is convex on $\mathbb{R}^{2}_{++}$.
    \item Determine whether or not $g(\textbf{y}) = \max_{x \in \mathbb{R}_{++}{2}} x_{1}y_{1} + x_{2}y_{2} - \sqrt{x_{1}x_{2}}$ is convex on $\mathbb{R}^2$
    \end{enumerate}
  \end{problem}
  \begin{solution}
  \end{solution}
\end{document}

